---
title: "Analysis_Manuscript"
author: "Jonas Paul Schoene"
date: "12/29/2020"
output: html_document
---

### Library/GGplot default settings/Clean Env

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(psych)
library(car)
library(Rmisc)
library(lubridate)
library(gridExtra)
library(effects)
library(MuMIn)
library(ggpubr)
options(scipen = 999)

theme_set(theme_bw())

rm(list = ls()) #Cleaning the R Environment, since the datasets are pretty big and can slow down the PC 
```

### Reading in the csv files 
```{r}
#Trump
df_t <-read.csv("data_annoymised/trump_anonymise_cleaned.csv") # this comes from runnig scriptes subfolder and is only first half

#Hillary Dataset
df_h <- read.csv("data_annoymised/hillary_anonymise_cleaned.csv")

#same-sex Marriage Dataset

df_g <- read.csv("data_annoymised/same_sex_anonymise_cleaned.csv")

#Fergusoen Dataset
df_f <- read.csv("data_annoymised/ferguson_anonymise_cleaned.csv")

# Creating Longformats for Valence of Situation Analysis

df_t_long <- df_t %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_t_long$intensity <- abs(df_t_long$intensity)

df_h_long <- df_h %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_h_long$intensity <- abs(df_h_long$intensity)

df_g_long <- df_g %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_g_long$intensity <- abs(df_g_long$intensity)

df_f_long <- df_f %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_f_long$intensity <- abs(df_f_long$intensity)
```

## Study 1

### Valence of the Situation. 

```{r}
### Trump = Positive

model1 = lmer(intensity ~ valence + (1|user_id), df_t_long); summary(model1)

confint.merMod(model1,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model1)

### Hill = Negative

model2 = lmer(intensity ~ valence + (1|user_id), df_h_long); summary(model2)

confint.merMod(model2,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model2)

```
### Predicting emotional language spread.

```{r}
# Trump
model3 = lmer(retweets_reciprocal ~  sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_t); summary(model3)

r.squaredGLMM(model3)

confint.merMod(model3,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

# Hill
model4 = lmer(retweets_reciprocal ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_h); summary(model4)

r.squaredGLMM(model4)

confint.merMod(model4,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
```

### Political affiliation analysis of users producing negative tweets.

```{r}
political_overview <- df_t %>% 
  dplyr::group_by(binary_affiliation) %>% 
  dplyr::summarise(n = n())
```
### Analysis of content of negative tweets. 

Due to data privacy we cannot include the content of the tweets which have been used for the topic analysis. Code for the topic modelling is in a seperate file.


## Study 2

### Valence of the Situation. 

```{r}
### Same-Sex = Positive

model5 = lmer(intensity ~ valence + (1|user_id), df_g_long); summary(model5)

confint.merMod(model5,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model5)

### Ferguson = Negative

model6 = lmer(intensity ~ valence + (1|user_id), df_f_long); summary(model6)

confint.merMod(model6,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model6)

```

### Predicting emotional language spread.

```{r}
# Same-Sex
model7 = lmer(retweets_reciprocal ~  sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_g); summary(model7)

r.squaredGLMM(model7)

confint.merMod(model7,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

# Ferguson 
model8 = lmer(retweets_reciprocal ~  sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_f); summary(model8)

r.squaredGLMM(model8)

confint.merMod(model8,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
```

### Political affiliation analysis of users producing negative tweets.

```{r}
political_overview <- df_g %>% 
  dplyr::group_by(binary_affiliation) %>% 
  dplyr::summarise(n = n())
```
### Analysis of content of negative tweets. 

Due to data privacy we cannot include the content of the tweets which have been used for the topic analysis. Code for the topic modelling is in a seperate file.

### Creating New MLM graphs

```{r}
# Trump
model3 = lmer(retweets_reciprocal ~  sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_t); summary(model3)

ee <- as.data.frame(Effect(c("sen_pos","sen_neg"),model3))
ee <- ee %>% 
  filter(sen_pos == 0 | sen_neg == 0)

ee$intensity <- ee$sen_pos+ee$sen_neg
first_row <- ee[1,]
ee <- rbind(ee,first_row)
ee$valence <- "sen_pos"
ee$valence[6:10] <- "sen_neg"


mlm_plot3 <- ggplot(ee, aes(x = intensity, y = fit, colour = valence))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_line(size = 1)+
  labs(x = "Emotional Intensity", y = "Number of Retweets 1-(reciprocal+1)", colour = "                ")+
  scale_color_manual(labels = c("Negative Language", "Positive Language"), values = c("red", "green3"))+
  ggtitle("Election win")+
  geom_ribbon(alpha=0.1, aes(ymin=lower,ymax=upper,colour = valence), linetype = 0,)+
  ylim(0.12, 0.20)

mlm_plot3

png("graphs/trump.png", width = 500, height = 300)
print(mlm_plot3)
dev.off()

# Hillary

model4 = lmer(retweets_reciprocal ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_h); summary(model4)

ee <- as.data.frame(Effect(c("sen_pos","sen_neg"),model4))
ee <- ee %>% 
  filter(sen_pos == 0 | sen_neg == 0)

ee$intensity <- ee$sen_pos+ee$sen_neg
first_row <- ee[1,]
ee <- rbind(ee,first_row)
ee$valence <- "sen_pos"
ee$valence[6:10] <- "sen_neg"


mlm_plot4 <- ggplot(ee, aes(x = intensity, y = fit, colour = valence))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_line(size = 1)+
  labs(x = "Emotional Intensity", y = "Number of Retweets 1-(reciprocal+1)", colour = "                ")+
  scale_color_manual(labels = c("Negative Language", "Positive Language"), values = c("red", "green3"))+
  ggtitle("Election loss")+
  geom_ribbon(alpha=0.1, aes(ymin=lower,ymax=upper,colour = valence), linetype = 0,)+
  ylim(0.12, 0.20)

mlm_plot4

png("graphs/hill.png", width = 500, height = 300)
print(mlm_plot4)
dev.off()

figure <- ggarrange(mlm_plot4, mlm_plot3,
                    labels = c("A", "B"),
                    ncol = 2, nrow = 1,
                    common.legend = TRUE)
figure

png("graphs/study2.png", width = 800, height = 400, res=100)
print(figure)
dev.off()


### same-sex
model7 = lmer(retweets_reciprocal ~  sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_g); summary(model7)

ee <- as.data.frame(Effect(c("sen_pos","sen_neg"),model7))
ee <- ee %>% 
  filter(sen_pos == 0 | sen_neg == 0)

ee$intensity <- ee$sen_pos+ee$sen_neg
first_row <- ee[1,]
ee <- rbind(ee,first_row)
ee$valence <- "sen_pos"
ee$valence[6:10] <- "sen_neg"


mlm_plot1 <- ggplot(ee, aes(x = intensity, y = fit, colour = valence))+
  geom_line(size = 1)+
  labs(x = "Emotional Intensity", y = "Number of Retweets 1-(reciprocal+1)", colour = "                 ")+
  scale_color_manual(labels = c("Negative Language", "Positive Language"), values = c("red", "green3"))+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Same-sex marriage")+
  geom_ribbon(alpha=0.1, aes(ymin=lower,ymax=upper,colour = valence), linetype = 0,)+
  ylim(0.10, 0.225)

mlm_plot1

png("graphs/same-sex.png", width = 500, height = 300)
print(mlm_plot1)
dev.off()

# Ferguson
model8 = lmer(retweets_reciprocal ~  sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_f); summary(model8)

ee <- as.data.frame(Effect(c("sen_pos","sen_neg"),model8))
ee <- ee %>% 
  filter(sen_pos == 0 | sen_neg == 0)

ee$intensity <- ee$sen_pos+ee$sen_neg
first_row <- ee[1,]
ee <- rbind(ee,first_row)
ee$valence <- "sen_pos"
ee$valence[6:10] <- "sen_neg"


mlm_plot2 <- ggplot(ee, aes(x = intensity, y = fit, colour = valence))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_line(size = 1)+
  labs(x = "Emotional Intensity", y = "Number of Retweets 1-(reciprocal+1)", colour = "                ")+
  scale_color_manual(labels = c("Negative Language", "Positive Language"), values = c("red", "green3"))+
  ggtitle("Ferguson unrest")+
  geom_ribbon(alpha=0.1, aes(ymin=lower,ymax=upper,colour = valence), linetype = 0,)+
  ylim(0.10, 0.225)

mlm_plot2 

png("graphs/ferg.png", width = 500, height = 300)
print(mlm_plot2)
dev.off()

figure <- ggarrange(mlm_plot2, mlm_plot1,
                    labels = c("A", "B"),
                    ncol = 2, nrow = 1,
                    common.legend = TRUE)
figure

png("graphs/study1.png", width = 800, height = 400, res=100)
print(figure)
dev.off()



```
