---
title: "article_results_supplementory_additions"
author: "Jonas Paul Schoene"
date: "3/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#libarys and default setting
```{r}
if(!require(Rmisc)) {install.packages("Rmisc"); require(Rmisc)}
if(!require(tidyverse)) {install.packages("tidyverse"); require(tidyverse)}
if(!require(lme4)) {install.packages("lme4"); require(lme4)}
if(!require(car)) {install.packages("car"); require(car)}
if(!require(odbc)) {install.packages("odbc"); require(odbc)}
if(!require(lmerTest)) {install.packages("lmerTest"); require(lmerTest)}
if(!require(RMySQL)) {install.packages("RMySQL"); require(RMySQL)}
if(!require(network)) {install.packages("network"); require(network)}
if(!require(effects)) {install.packages("effects"); require(effects)}
if(!require(MuMIn)) {install.packages("MuMIn"); require(MuMIn)}
if(!require(pscl)) {install.packages("pscl"); require(pscl)}
if(!require(nlme)) {install.packages("nlme"); require(nlme)}
if(!require(glmmTMB)) {install.packages("glmmTMB"); require(glmmTMB)}
if(!require(MASS)) {install.packages("MASS"); require(MASS)}
if(!require(gamm4)) {install.packages("gamm4"); require(gamm4)}
if(!require(vader)) {install.packages("vader"); require(vader)}
if(!require(lmtest)) {install.packages("lmtest"); require(lmtest)}

rm(list = ls()) #Cleaning the R Environment, since the datasets are pretty big and can slow down the PC 

theme_set(theme_bw()) #simple black and white design

options(scipen = 999) # removes the e^n appreviations
```
# STUDY 1

## Hillary Dataset

```{r}
df_h <-read.csv("data_annoymised/hillary_anonymise_cleaned.csv")

df_h <- df_h[!duplicated(df_h), ]

df_h_long <- df_h %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_h_agg <- df_h %>% # THIS IS THE SOLUTION
  dplyr::group_by(user_id) %>% 
  dplyr::summarise(sen_neg = mean(sen_neg),
            sen_pos = mean(sen_pos),
            retweets_log = mean(retweets_log),
            followers = mean(followers),
            followers_log = max(followers_log),
            retweets = round(mean(exp(retweets_log - 1))))

plot(density(df_h$retweets_reciprocal))

```

# Hypothesis 1.) Categorizing Events

```{r}
### Hillary = Negative

model_h = lmer(intensity ~ valence + (1|user_id), df_h_long); summary(model_h)

#confint.merMod(model_h,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model_h)
```

# Hypothesis 2.) Spread of Negativity

```{r}
# Log + 1

model_h0 = lmer(retweets_reciprocal ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_h); summary(model_h0)

model_h1 = lmer(retweets_log ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_h); summary(model_h1)

model_h2 = glmer(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), family = poisson(link = "log"), df_h); summary(model_h2)

model_h3 = glmer.nb(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_h); summary(model_h3)

lrtest(model_h0,model_h1,model_h2,model_h3)

anova(model_h0,model_h1,model_h2,model_h3)

```

# Generalized Additive Mixed Models

```{r}
model_h5 <- gamm4(retweets_reciprocal ~ s(sen_pos, k = 4) + s(sen_neg, k = 4) + followers_log, family=gaussian, random= ~ (1|user_id), data = df_h)

summary(model_h5$gam)
summary(model_h5$mer)

plot(model_h5$gam, pages=1, all.terms = TRUE)

```
# Vader vs SentiStrenght

```{r}
cor.test(df_h$sen_pos, df_h$vader_pos)
cor.test(df_h$sen_neg, df_h$vader_neg)
```

## Trump Dataset

```{r}
df_t <-read.csv("data_annoymised/trump_anonymise_cleaned.csv")

df_t <- df_t[!duplicated(df_t), ]

df_t_long <- df_t %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_t_agg <- df_t %>% # THIS IS THE SOLUTION
  dplyr::group_by(user_id) %>% 
  dplyr::summarise(sen_neg = mean(sen_neg),
            sen_pos = mean(sen_pos),
            retweets_log = mean(retweets_log),
            followers = mean(followers),
            followers_log = max(followers_log),
            retweets = round(mean(exp(retweets_log - 1))))

plot(density(df_t$retweets_reciprocal))

```

# Hypothesis 1.) Categorizing Events

```{r}
### Trump = Positive

model_t = lmer(intensity ~ valence + (1|user_id), df_t_long); summary(model_t)

#confint.merMod(model_t,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model_t)
```

# Hypothesis 2.) Spread of Negativity

```{r}
# Log + 1

model_t0 = lmer(retweets_reciprocal ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_t); summary(model_t0)

model_t1 = lmer(retweets_log ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_t); summary(model_t1)

model_t2 = glmer(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), family = poisson(link = "log"), df_t); summary(model_t2)

model_t3 = glmer.nb(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_t); summary(model_t3)

lrtest(model_t0,model_t1,model_t2,model_t3)

anova(model_t0,model_t1,model_t2,model_t3)

```

# Generalized Additive Mixed Models

```{r}
model_t5 <- gamm4(retweets_reciprocal ~ s(sen_pos, k = 4) + s(sen_neg, k = 4) + followers_log, family=gaussian, random= ~ (1|user_id), data = df_t)

summary(model_t5$gam)
summary(model_t5$mer)

plot(model_t5$gam, pages=1, all.terms = TRUE)

```

# Vader vs SentiStrenght

```{r}
cor.test(df_t$sen_pos, df_t$vader_pos)
cor.test(df_t$sen_neg, df_t$vader_neg)
```


## Study 2

# Ferguson Dataset

```{r}
df_f <-read.csv("data_annoymised/ferguson_anonymise_cleaned.csv")

df_f <- df_f[!duplicated(df_f), ]

df_f_long <- df_f %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_f_agg <- df_f %>% # THIS IS THE SOLUTION
  dplyr::group_by(user_id) %>% 
  dplyr::summarise(sen_neg = mean(sen_neg),
            sen_pos = mean(sen_pos),
            retweets_log = mean(retweets_log),
            followers = mean(followers),
            followers_log = max(followers_log),
            retweets = round(mean(exp(retweets_log - 1))))

plot(density(df_f$retweets_reciprocal))

```

# Hypothesis 1.) Categorizing Events

```{r}
### Ferguson = Negative

model_f = lmer(intensity ~ valence + (1|user_id), df_f_long); summary(model_f)

#confint.merMod(model_f,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model_f)
```

# Hypothesis 2.) Spread of Negativity

```{r}
# Log + 1

model_f0 = lmer(retweets_reciprocal ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_f); summary(model_f0)

model_f1 = lmer(retweets_log ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_f); summary(model_f1)

model_f2 = glmer(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), family = poisson(link = "log"), df_f); summary(model_f2)

model_f3 = glmer.nb(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_f); summary(model_f3)

lrtest(model_f0,model_f1,model_f2,model_f3)

anova(model_f0,model_f1,model_f2,model_f3)

```

# Generalized Additive Mixed Models

```{r}
model_f5 <- gamm4(retweets_reciprocal ~ s(sen_pos, k = 4) + s(sen_neg, k = 4) + followers_log, family=gaussian, random= ~ (1|user_id), data = df_f)

summary(model_f5$gam)
summary(model_f5$mer)

plot(model_f5$gam, pages=1, all.terms = TRUE)

```

# Vader vs SentiStrenght

```{r}
cor.test(df_f$sen_pos, df_f$vader_pos)
cor.test(df_f$sen_neg, df_f$vader_neg)
```



# Same-Sex Dataset

```{r}
df_g <-read.csv("data_annoymised/same_sex_anonymise_cleaned.csv")

df_g <- df_g[!duplicated(df_g), ]

df_g_long <- df_g %>% 
  gather(valence, intensity, sen_pos, sen_neg)

df_g_agg <- df_g %>% # THIS IS THE SOLUTION
  dplyr::group_by(user_id) %>% 
  dplyr::summarise(sen_neg = mean(sen_neg),
            sen_pos = mean(sen_pos),
            retweets_log = mean(retweets_log),
            followers = mean(followers),
            followers_log = max(followers_log),
            retweets = round(mean(exp(retweets_log - 1))))

plot(density(df_g$retweets_reciprocal))

```

# Hypothesis 1.) Categorizing Events

```{r}
### Same-Sex = Positive

model_g = lmer(intensity ~ valence + (1|user_id), df_g_long); summary(model_g)

#confint.merMod(model_g,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)

r.squaredGLMM(model_g)
```

# Hypothesis 2.) Spread of Negativity

```{r}
# Log + 1

model_g0 = lmer(retweets_reciprocal ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_g); summary(model_g0)

model_g1 = lmer(retweets_log ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_g); summary(model_g1)

model_g2 = glmer(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), family = poisson(link = "log"), df_g); summary(model_g2)

model_g3 = glmer.nb(retweets ~ sen_pos + sen_neg + sen_pos:sen_neg + scale(followers_log) + (1|user_id), df_g); summary(model_g3)

lrtest(model_g0,model_g1,model_g2,model_g3)

anova(model_g0,model_g1,model_g2,model_g3)

```

# Generalized Additive Mixed Models

```{r}
model_g5 <- gamm4(retweets_reciprocal ~ s(sen_pos, k = 4) + s(sen_neg, k = 4) + followers_log, family=gaussian, random= ~ (1|user_id), data = df_g)

summary(model_g5$gam)
summary(model_g5$mer)

plot(model_g5$gam, pages=1, all.terms = TRUE)

```

# Vader vs SentiStrenght

```{r}
cor.test(df_g$sen_pos, df_g$vader_pos)
cor.test(df_g$sen_neg, df_g$vader_neg)
```
# Vader vs SentiStrenght Main Hypothesis comperison

```{r}
model_hv = lmer(retweets_reciprocal ~ vader_pos + vader_neg + vader_pos:vader_neg + scale(followers_log) + (1|user_id), df_h); summary(model_hv)

confint.merMod(model_hv,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
r.squaredGLMM(model_hv)

anova(model_h0, model_hv)
lrtest(model_h0, model_hv)

model_tv = lmer(retweets_reciprocal ~ vader_pos + vader_neg + vader_pos:vader_neg + scale(followers_log) + (1|user_id), df_t); summary(model_tv)

confint.merMod(model_tv,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
r.squaredGLMM(model_tv)

anova(model_t0, model_tv)
lrtest(model_t0, model_tv)

model_fv = lmer(retweets_reciprocal ~ vader_pos + vader_neg + vader_pos:vader_neg + scale(followers_log) + (1|user_id), df_f); summary(model_fv)

confint.merMod(model_fv,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
r.squaredGLMM(model_f)

anova(model_f0, model_fv)
lrtest(model_f0, model_fv)

model_gv = lmer(retweets_reciprocal ~ vader_pos + vader_neg + vader_pos:vader_neg + scale(followers_log) + (1|user_id), df_g); summary(model_gv)

confint.merMod(model_gv,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
r.squaredGLMM(model_gv)

anova(model_g0, model_gv)
lrtest(model_g0, model_gv)
```


# Saving Density Plots

```{r}
# Trump
trump_density <- ggplot(df_t, aes(x=retweets_reciprocal)) + 
  geom_density()+
  ggtitle("Election win")

trump_density

# Hillary
hillary_density <- ggplot(df_h, aes(x=retweets_reciprocal)) + 
  ggtitle("Election loss")+
  geom_density()
hillary_density

# Same-sex
same_sex_density <- ggplot(df_g, aes(x=retweets_reciprocal)) + 
  ggtitle("Same-sex marriage")+
  geom_density()
same_sex_density

# Ferguson
ferguson_density <- ggplot(df_f, aes(x=retweets_reciprocal)) + 
  geom_density()+
  ggtitle("Ferguson unrest")

ferguson_density

figure <- ggarrange(hillary_density, trump_density,same_sex_density,ferguson_density,
                    labels = c("A", "B","C","D"),
                    ncol = 2, nrow = 2,
                    common.legend = TRUE)
figure

png("graphs/density.png", width = 800, height = 400, res=100)
print(figure)
dev.off()

```

# Confidence intervalls
```{r}
# Trump

model_t0_conf <- confint.merMod(model_t0,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_t0_r <-r.squaredGLMM(model_t0)
model_t1_conf <-confint.merMod(model_t1,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_t1_r <- r.squaredGLMM(model_t1)
model_t2_conf <-confint.merMod(model_t2,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_t2_r <- r.squaredGLMM(model_t2)
model_t3_conf <-confint.merMod(model_t3,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_t3_r <- r.squaredGLMM(model_t3)

# Hillary

model_h0_conf <- confint.merMod(model_h0,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_h0_r <-r.squaredGLMM(model_h0)
model_h1_conf <-confint.merMod(model_h1,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_h1_r <- r.squaredGLMM(model_h1)
model_h2_conf <-confint.merMod(model_h2,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_h2_r <- r.squaredGLMM(model_h2)
model_h3_conf <-confint.merMod(model_h3,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_h3_r <- r.squaredGLMM(model_h3)

# Same-sex

model_g0_conf <- confint.merMod(model_g0,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_g0_r <-r.squaredGLMM(model_g0)
model_g1_conf <-confint.merMod(model_g1,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_g1_r <- r.squaredGLMM(model_g1)
model_g2_conf <-confint.merMod(model_g2,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_g2_r <- r.squaredGLMM(model_g2)
model_g3_conf <-confint.merMod(model_g3,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_g3_r <- r.squaredGLMM(model_g3)

# Ferguson

model_f0_conf <- confint.merMod(model_f0,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_f0_r <-r.squaredGLMM(model_f0)
model_f1_conf <-confint.merMod(model_f1,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_f1_r <- r.squaredGLMM(model_f1)
model_f2_conf <-confint.merMod(model_f2,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_f2_r <- r.squaredGLMM(model_f2)
model_f3_conf <-confint.merMod(model_f3,level = 0.95, method = "boot", boot.type = "perc", nsim = 100, oldNames = F)
model_f3_r <- r.squaredGLMM(model_f3)

```